EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-30 05_examples.tex

\section{Examples}\label{SecExamples}
In this section we illustrate the functioning of the \NAME
library and their interfaces as solver for DMFT through a variety of examples, including
discussion of relevant code snippets. As some tasks are inherently agnostic on the impurity
solver (and the impurity solver is agnostic about them), the user is expected to implement
them, or interface to existing utilities. For instance, all the Fortran subroutines with 
naming convention \texttt{dmft\_do\_something()} refer to implementations that can be found
in the {DMFTtools} package\footnote{\url{https://github.com/aamaricci/DMFTtools}},
the example based on w2dynamics relies on the internal facilities provided by the \texttt{DMFT.py} script \cite{Wallerberger2019CPC} and the TRIQS library provides an 
extensive toolbox for the manipulation of Green's functions and related quantities
\cite{Parcollet2015CPC}.

@@

\setbox0=\hbox{%
  \begin{minipage}{0.465\linewidth}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
program ed_hm_bethe
   USE EDIPACK
   USE SCIFOR
   implicit none
   integer                :: Le=1000
   real(8)                :: wmixing=0.5d0
   real(8)                :: D=1d0
   integer                :: Nb
   real(8),allocatable    :: Bath(:)
   complex(8),allocatable :: Hloc(:,:,:,:)
   real(8),allocatable    :: Ebands(:),Dbands(:)
   complex(8),allocatable :: Smats(:,:,:,:,:)
   complex(8),allocatable :: Delta(:,:,:,:,:)
   !...  
   !Read variables
   call ed_read_input('inputED.conf')
   !Solver-specific arays
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Initialize Bethe arrays
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !Set local H
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
}
\savestack{\listingA}{\box0}

\setbox0=\hbox{%
  \begin{minipage}{0.505\linewidth}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
!...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;
//Read  variables    
char input[] = "inputED.conf"; 
read_input(input);      
//Dimensions
int64_t d[4] = {Nspin,Nspin,Norb,Norb};
int total_size = d[0] * d[1] * d[2] * d[3];
int total_size_n5 = total_size * Lmats;    
// Solver-specific arrays
vector<complex<double>> Hloc(total_size);
vector<complex<double>> Smats(total_size_n5);
vector<complex<double>> Delta(total_size_n5);
...
// Initialize Bethe arrays
vector<double> Ebands, Dbands;
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);
//set local H
ed_set_Hloc_single_N4(Hloc.data(), d);
\end{lstlisting}
\end{minipage}
}
\savestack{\listingB}{\box0}

@@

\item[{\tiny {\it User}}] Evaluate the local interacting Green's function
  $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.

@@

\setbox0=\hbox{%
  \begin{minipage}{0.45\linewidth}
    \center
    \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
!DMFT loop
do while(.not.converged.AND.iloop<nloop)
    iloop=iloop+1     
    ! Call ED Solver
    call ed_solve(bath)     
    ! Retrieve Self-energy on Matsubara axis
    call ed_get_sigma(Smats,'m')
    ! Build local Green's function
    wfreq = pi/beta*(2*arange(1,Lmats)-1)
    do i=1,Lmats
       zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
       Gmats(1,1,1,1,i)=sum(DOS/(zeta-Ene))*de  
    enddo
    ! Self-consistency
    Delta = D/4d0*Gmats
    ! Fitting -> new bath
    call ed_chi2_fitgf(Weiss,bath,ispin=1)     
    ! Check convergence
    converged=check_convergence(Delta,&
          dmft_error,Nsuccess,Nloop)
enddo
\end{lstlisting}
\end{minipage}
}
\savestack{\listingA}{\box0}

\setbox0=\hbox{%
  \begin{minipage}{0.52\linewidth}
    \center
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
  // DMFT loop
  while (iloop < Nloop && !converged) {
    //  Call ED Solver
    solve_site(Bath.data(),bath_dim,1,1);      
    // Retrieve  Self-energy on Matsubara axis
    get_sigma_site_n5(Smats.data(),//
        0,0,wm.data(),Lmats,0);
    //  Build a local Green's function:
    for (int i=0;i<Lmats;++i) {
      zeta= wm[i] + xmu - Smats[i];
      Gmats[i] = complex<double>(0.0,0.0);
      for (int j=0; j< Le; j++) {
        Gmats[i]+=Dbands[j]/(zeta-Ebands[j]);
      }
    }
    // Self-consistency
    for (int i = 0; i < Lmats; ++i) {
      Delta[i] = 0.25 * D * Gmats[i];
    }
    // Fit -> new bath
    chi2_fitgf_single_normal_n5(Delta.data(),//
        delta_dim,Bath.data(),bath_dim,1,0,1);
    // Check convergence
    converged = check_convergence(Delta,//
        dmft_error, Nsuccess, Nloop, comm);  
  }
\end{lstlisting}
\end{minipage}
}
\savestack{\listingB}{\box0}

@@

Thus, here we illustrate the DMFT solution of the excitonic phase as a way to
illustrate the ability of \NAME to capture matter phases with lowered
spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
  bath\_type=replica}.
\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   !> Set $H_\mathrm{loc}$
   allocate(Hloc(Nso,Nso))
   Hloc = sum(Hk,dim=3)/Lk
   where(abs(dreal(Hloc))<1d-6)Hloc=zero
   call ed_set_hloc(Hloc)
   !> Setup the replica bath basis:
   allocate(lambdasym_vector(Nbath,4))
   allocate(Hsym_basis(Nso,Nso,4))
   Hsym_basis(:,:,1)=Gamma03  ;lambdasym_vector(:,1)= Mh
   Hsym_basis(:,:,2)=Gamma01 ;lambdasym_vector(:,2)= sb_field
   Hsym_basis(:,:,3)=Gamma31 ;lambdasym_vector(:,3)= sb_field
   Hsym_basis(:,:,4)=Gamma11 ;lambdasym_vector(:,4)=-sb_field
   !> Set the replica bath
   call ed_set_Hreplica(Hsym_basis,lambdasym_vector)
   !> Get bath dimension and allocate user bath to this size
   Nb=ed_get_bath_dimension(4)   !There are 4 symmetries
   allocate(Bath(Nb))
   !
   !> Initialize the ED solver (bath is guessed or read from file) 
   call ed_init_solver(bath)
\end{lstlisting}
where we use the local non-interacting Hamiltonian 
$H_\mathrm{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
$h^0_{\a\b\s\s'}$, i.e. the impurity Hamiltonian. To anticipate the
possibility of forming an excitonic ordered phase, the replica bath
is constructed out of matrix basis with 4 distinct elements
$\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which
are proportional, respectively, to the mass term, the exciton singlet
$E_0$, the exciton triplet along easy-axis $E_z$ and in-plane
$E_x$ (we assume $E_y=0$ levaraging on residual $U(1)$ in-plane
symmetry.

In the following we consider the case of $M=1$ which corresponds to a
QSHI in the non-interacting limit and $J/U=0.25$.
The implemention is nearly identical to the cases discussed above and
we report it here for completeness:
\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   iloop=0;converged=.false.
   do while(.not.converged.AND.iloop<nloop)
     iloop=iloop+1
     !> Solve the impurity problem, retrieve $\Sigma(i\omega)$
     call ed_solve(bath)
     call ed_get_sigma(Smats,axis='mats')
     !> Get $G_\mathrm{loc}$ (assume to have a function for this task)
     call get_gloc(Hk,Gmats,Smats,axis='m')
     !> Update the Weiss field $\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma$ +  Linear mixing.
     call dmft_self_consistency(Gmats,Smats,Weiss)
     if(iloop>1)Weiss = wmixing*Weiss + (1.d0-wmixing)*Weiss_;Weiss_=Weiss
     !> Fit to updated the bath
     call ed_chi2_fitgf(Weiss,bath,ispin=1)
     !Check convergence (using DMFT_TOOLS)
     converged = check_convergence(Weiss(1,1,:),dmft_error,nsuccess,nloop)
   enddo  
\end{lstlisting}

@@

The essential features of the groundstate phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
at the Fermi level renders ineffective the logarithmic instability, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
With a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology. Furthermore, the long-range ordering 
eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRBa,Rachel2010PRB} and
later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
simulations \cite{Hohenadler2013ROPIP}.

@@

\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   iloop=0;converged=.false.
   do while(.not.converged.AND.iloop<nloop)
      iloop=iloop+1
      !
      !> Solve the two inequivalent impurity problems
      if(neelsym)then
        !> solve just one sublattice and get the other by Neel symmetry
        call ed_solve(Bath(1,:))
        call ed_get_sigma_matsubara(Smats(1,:,:,:,:,:))
        select case(ansatz)
            case('off-plane')
             Smats(2,2,2,:,:,:) = Smats(1,1,1,:,:,:) 
             Smats(2,1,1,:,:,:) = Smats(1,2,2,:,:,:) 
             if(master)write(*,*) ">>> Enforcing AFMz symmetry"
            case('in-plane')
             Smats(2,1,1,:,:,:) = Smats(1,1,1,:,:,:)   
             Smats(2,2,2,:,:,:) = Smats(1,2,2,:,:,:)   
             Smats(2,1,2,:,:,:) = -Smats(1,1,2,:,:,:)  
             Smats(2,2,1,:,:,:) = -Smats(1,2,1,:,:,:) 
             if(master)write(*,*) ">>> Enforcing AFMx symmetry"
        end select
      else
         !> solve both sublattices independently with the RDMFT wrapper:
         !  mpi_lanc=T => MPI lanczos, mpi_lanc=F => MPI for ineq sites
         call ed_solve(Bath,mpi_lanc=.true.)
         !> retrieve all self-energies:
         call ed_get_sigma_matsubara(Smats,Nineq)
         !
      endif
      !
      !> Compute the local Green's function
      call dmft_gloc_matsubara(Hk,Gmats,Smats)
      !
      !> Compute the two inequivalent Weiss fields
      call dmft_self_consistency(Gmats,Smats,Weiss)
      !
      !> Fit the new bath
      !  this behaves differently depending on the ed_mode input:
      !  - for the normal mode: normal/AFMz phase is solved, so we 
      !    can fit spin1 and spin2 components independently
      !  - for the nonsu2 mode: Sz-conservation can be broken, so a 
      !    unique fit for both spin components is needed
      select case(ed_mode)
       case("normal")
         call ed_chi2_fitgf(Bath,Weiss,ispin=1)
         call ed_chi2_fitgf(Bath,Weiss,ispin=2)
       case("nonsu2")
         call ed_chi2_fitgf(Bath,Weiss,Hloc)
      end select
      !
      !> linear mixing (aids convergence near transition points)
      if(iloop>1) Bath = wmixing*Bath + (1.d0-wmixing)*Bath_prev
      Bath_prev = Bath
      !
      !> check convergence
      converged = check_convergence(Weiss(:,1,1,1,1,:),dmft_error,nsuccess,nloop)
      !
   enddo
   !
   !> Compute Kinetic Energy
   call dmft_kinetic_energy(Hk,Smats)
\end{lstlisting}

>>>>

\section{Examples}\label{SecExamples}
In this section we illustrate and benchmark the functionalities and of the \NAME
library and its interfaces as solver for DMFT through a variety of examples. We also discuss in detailed the relevant code snippets from different programming languages. 
Some tasks --particularly those associated to the implementation of the DMFT self-consistency--  are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
In the implementation using Fortran, Python or other \NAME API we adopt a reverse communication strategy, which requires the user to independently implement these parts or, equivalently, to exploit existing utilities. 
In our examples based on the Fortran APIs  we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors) to perform specific tasks, including the evaluation of the local Green's function, the implementation of the self-consistency, the construction of the tight-binding model or the calculation of the kinetic energy. 
Where appropriate, we include comments that reference these external procedures.
On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself—see the \texttt{DMFT.py} script~\cite{Wallerberger2019CPC}—which handles all these tasks seamlessly.
Similarly, the TRIQS library offers an extensive toolbox for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.

@@

\setbox0=\hbox{%
  \begin{minipage}{0.465\linewidth}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
program ed_hm_bethe
   USE EDIPACK
   USE SCIFOR
   implicit none
   integer                :: Le=1000
   real(8)                :: wmixing=0.5d0
   real(8)                :: D=1d0
   integer                :: Nb
   real(8),allocatable    :: Bath(:)
   complex(8),allocatable :: Hloc(:,:,:,:)
   real(8),allocatable    :: Ebands(:),Dbands(:)
   complex(8),allocatable :: Smats(:,:,:,:,:)
   complex(8),allocatable :: Delta(:,:,:,:,:)
   !...  
   !Read variables
   call ed_read_input('inputED.conf')
   !Solver-specific arays
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Initialize Bethe arrays
   allocate(Ebands(Le),Dbands(Le))
   !From SciFortran:
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !Set local H
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
}
\savestack{\listingA}{\box0}

\setbox0=\hbox{%
  \begin{minipage}{0.505\linewidth}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
!...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;
//Read  variables    
char input[] = "inputED.conf"; 
read_input(input);      
//Dimensions
int64_t d[4] = {Nspin,Nspin,Norb,Norb};
int total_size = d[0] * d[1] * d[2] * d[3];
int total_size_n5 = total_size * Lmats;    
// Solver-specific arrays
vector<complex<double>> Hloc(total_size);
vector<complex<double>> Smats(total_size_n5);
vector<complex<double>> Delta(total_size_n5);
...
// Initialize Bethe arrays
vector<double> Ebands, Dbands;
//Locally defined functions:
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);
//set local H
ed_set_Hloc_single_N4(Hloc.data(), d);
\end{lstlisting}
\end{minipage}
}
\savestack{\listingB}{\box0}

@@

\item[{\tiny {\it User}}] Evaluate the local interacting Green's function
$$
G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e
$$ 
with  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.

@@

\setbox0=\hbox{%
  \begin{minipage}{0.46\linewidth}
    \center
    \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
    !DMFT loop
do while(.not.converged.AND.iloop<nloop)
    iloop=iloop+1     
    !Call ED Solver
    call ed_solve(bath)     
    !Retrieve $\Sigma(i\omega_n)$
    call ed_get_sigma(Smats,'m')
    !Build local Green's function
    wfreq = pi/beta*(2*arange(1,Lmats)-1)
    do i=1,Lmats
       zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
       Gmats(1,1,1,1,i)=sum(DOS/(zeta-Ene))*de  
    enddo
    !Self-consistency
    Delta = D/4d0*Gmats
    !Fitting -> new bath
    call ed_chi2_fitgf(Weiss,bath,ispin=1)     
    !Check convergence: from $\mathrm{DMFTtools}$
    converged=check_convergence(Delta,&
          dmft_error,Nsuccess,Nloop)
enddo
\end{lstlisting}
\end{minipage}
}
\savestack{\listingA}{\box0}

\setbox0=\hbox{%
  \begin{minipage}{0.51\linewidth}
    \center
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
//DMFT loop
while (iloop < Nloop && !converged) {
  //Call ED Solver
  solve_site(Bath.data(),bath_dim,1,1);      
  //Retrieve $\Sigma(i\omega_n)$
  get_sigma_site_n5(Smats.data(),//
      0,0,wm.data(),Lmats,0);
  //Build a local Green's function:
  for (int i=0;i<Lmats;++i) {
    zeta= wm[i] + xmu - Smats[i];
    Gmats[i] = complex<double>(0.0,0.0);
    for (int j=0; j< Le; j++) {
      Gmats[i]+=Dbands[j]/(zeta-Ebands[j]);
    }
  }
  //Self-consistency
  for (int i = 0; i < Lmats; ++i) {
    Delta[i] = 0.25 * D * Gmats[i];
  }
  //Fit -> new bath
  chi2_fitgf_single_normal_n5(Delta.data(),//
      delta_dim,Bath.data(),bath_dim,1,0,1);
  //Check convergence: local functions
  converged = check_convergence(Delta,//
      dmft_error, Nsuccess, Nloop, comm);  
}
\end{lstlisting}
\end{minipage}
}
\savestack{\listingB}{\box0}

@@

Thus, here we illustrate the DMFT solution of the excitonic phase as a way to
illustrate the ability of \NAME to capture matter phases with lowered
spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
  bath\_type=replica}.
\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   !> Set $H_\mathrm{loc}$
   allocate(Hloc(Nso,Nso))
   Hloc = sum(Hk,dim=3)/Lk
   where(abs(dreal(Hloc))<1d-6)Hloc=zero
   call ed_set_hloc(Hloc)
   !> Setup the replica bath basis:
   allocate(lambdasym_vector(Nbath,4))
   allocate(Hsym_basis(Nso,Nso,4))
   Hsym_basis(:,:,1)=Gamma03  ;lambdasym_vector(:,1)= Mh
   Hsym_basis(:,:,2)=Gamma01 ;lambdasym_vector(:,2)= sb_field
   Hsym_basis(:,:,3)=Gamma31 ;lambdasym_vector(:,3)= sb_field
   Hsym_basis(:,:,4)=Gamma11 ;lambdasym_vector(:,4)=-sb_field
   !> Set the replica bath
   call ed_set_Hreplica(Hsym_basis,lambdasym_vector)
   !> Get bath dimension and allocate user bath to this size
   Nb=ed_get_bath_dimension(4)   !There are 4 symmetries
   allocate(Bath(Nb))
   !
   !> Initialize the ED solver (bath is guessed or read from file) 
   call ed_init_solver(bath)
\end{lstlisting}
where we use the local non-interacting Hamiltonian 
$H_\mathrm{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
$h^0_{\a\b\s\s'}$, i.e. the impurity Hamiltonian. To anticipate the
possibility of forming an excitonic ordered phase, the replica bath
is constructed out of matrix basis with 4 distinct elements
$\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which
are proportional, respectively, to the mass term, the exciton singlet
$E_0$, the exciton triplet along easy-axis $E_z$ and in-plane
$E_x$ (we assume $E_y=0$ levaraging on residual $U(1)$ in-plane
symmetry. 
%
In the following we consider the case of $M=1$ which corresponds to a
QSHI in the non-interacting limit and $J/U=0.25$.
The implemention is nearly identical to the cases discussed above and
we report it here for completeness:
\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   iloop=0;converged=.false.
   do while(.not.converged.AND.iloop<nloop)
     iloop=iloop+1
     !> Solve the impurity problem, retrieve $\Sigma(i\omega)$
     call ed_solve(bath)
     call ed_get_sigma(Smats,axis='mats')
     !> Get $G_\mathrm{loc}$ using $\color{comment-color}\mathrm{DMFTtools}$
     call get_gloc(Hk,Gmats,Smats,axis='m')
     !> Update the Weiss field ${\color{comment-color}\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma}$ +  Linear mixing: using $\color{comment-color}\mathrm{DMFTtools}$
     call dmft_self_consistency(Gmats,Smats,Weiss)
     if(iloop>1)Weiss = wmixing*Weiss + (1.d0-wmixing)*Weiss_;Weiss_=Weiss
     !> Fit to updated the bath
     call ed_chi2_fitgf(Weiss,bath,ispin=1)
     !Check convergence: using $\color{comment-color}\mathrm{DMFTtools}$
     converged = check_convergence(Weiss(1,1,:),dmft_error,nsuccess,nloop)
   enddo  
\end{lstlisting}

@@

The essential features of the groundstate phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
at the Fermi level renders ineffective the logarithmic instability, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
With a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology. Furthermore, the long-range ordering 
eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and there were two references to the same paper
later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
simulations \cite{Hohenadler2013ROPIP}.

@@

\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
   iloop=0;converged=.false.
   do while(.not.converged.AND.iloop<nloop)
      iloop=iloop+1
      !
      !> Solve the two inequivalent impurity problems
      if(neelsym)then
        !> solve just one sublattice and get the other by Neel symmetry
        call ed_solve(Bath(1,:))
        call ed_get_sigma(Smats(1,:,:,:,:,:),axis='m')
        select case(ansatz)
            case('off-plane')
             Smats(2,2,2,:,:,:) = Smats(1,1,1,:,:,:) 
             Smats(2,1,1,:,:,:) = Smats(1,2,2,:,:,:) 
             if(master)write(*,*) ">>> Enforcing AFMz symmetry"
            case('in-plane')
             Smats(2,1,1,:,:,:) = Smats(1,1,1,:,:,:)   
             Smats(2,2,2,:,:,:) = Smats(1,2,2,:,:,:)   
             Smats(2,1,2,:,:,:) = -Smats(1,1,2,:,:,:)  
             Smats(2,2,1,:,:,:) = -Smats(1,2,1,:,:,:) 
             if(master)write(*,*) ">>> Enforcing AFMx symmetry"
        end select
      else
         !> solve both sublattices independently using EDIpack2ineq:
         !  mpi_lanc=T => MPI lanczos, mpi_lanc=F => MPI for ineq sites
         call ed_solve(Bath,mpi_lanc=.true.)
         !> retrieve all self-energies:
         call ed_get_sigma(Smats,Nineq,axis='m')
         !
      endif
      !
      !> Get ${\color{comment-color}G_{loc}(i\omega_n) }$ : using ${\color{comment-color}\mathrm{DMFTtools}}$
      call dmft_gloc_matsubara(Hk,Gmats,Smats)
      !
      !> Update local Weiss fields ${\color{comment-color}\GG^{-1}_0 = G_{loc} + \Sigma}$ :using ${\color{comment-color}\mathrm{DMFTtools}}$
      call dmft_self_consistency(Gmats,Smats,Weiss)
      !
      !> Fit the new bath:
      !  - normal mode: normal/AFMz and we fit spin-components independently
      !  - nonsu2 mode: broken Sz-conservation and we fit both spin components altogether
      select case(ed_mode)
       case("normal")
         call ed_chi2_fitgf(Bath,Weiss,ispin=1)
         call ed_chi2_fitgf(Bath,Weiss,ispin=2)
       case("nonsu2")
         call ed_chi2_fitgf(Bath,Weiss,Hloc)
      end select
      !
      !> linear mixing and check convergence: using ${\color{comment-color}\mathrm{DMFTtools}}$
      if(iloop>1) Bath = wmixing*Bath + (1.d0-wmixing)*Bath_prev
      Bath_prev = Bath
      converged = check_convergence(Weiss(:,1,1,1,1,:),dmft_error,nsuccess,nloop)
      !
   enddo
   !
   !> Compute Kinetic Energy: using ${\color{comment-color}\mathrm{DMFTtools}}$
   call dmft_kinetic_energy(Hk,Smats)
\end{lstlisting}
